A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-07-25 elsfrontmatter.tex
add detlef as author
edits to abstrct

\author[nies]{Shinichiro Fujimori}
\author[pbl]{Maarten van den Berg}
\author[pik]{David Klein}
\author[pnnl]{Steven J. Smith}
\author[iiasa]{Keywan Riahi}

@@

\begin{abstract}
Harmonization describes the process required to match Integrated Assessment
Model (IAM) GHG and air pollutants results against a common source of historical
emissions trajectories. To date, harmonization has been performed separately by
individual modeling teams through
% * <maarten.vandenberg@pbl.nl> 2017-07-03T20:19:43.403Z:
% 
% IMAGE has provided harmonized emissions in the past, generated by a harmonization routine applying a ratio convergence method (on a higher aggregation level) (Hof et al., 2016). I think the contrast with these harmonization approaches and this work, which enables a documented, automated process selecting appropriate harmonization methodologies, might not be clear. Furthermore, later in the text cross-model harmonization methods (though less sophisticated) are mentioned. It is worth mentioning that previous approaches are far less sophisticated.
% 
% ^.
% * <sfujimori112256@gmail.com> 2017-05-24T19:26:26.142Z:
% 
% > harmonization has been performed separately by individual modeling teams 
% I think harmonization is not done. We just report the direct model outputs.
% 
% One of the ways to  make the background is that earlier IPCC scenarios (SRES and RCPs) did not document the harmonization method and far from transparent.
% 
% ^.
the use of expert opinion and solicitation. In order to support ongoing and
future global climate and socioeconomic analyses, incorporate model advancements
towards more complex regional and sectoral representations, and expand the
capability of modeling teams to participate in intercomparison exercises, an
automated approach to choosing harmonization methods becomes necessary. This
work describes a novel
% * <sfujimori112256@gmail.com> 2017-05-24T20:13:08.493Z:
% 
% > novel
% It would be better to stress how novel and useful.
% 
% ^.
methodology for determining such harmonization methods and an open-source Python
software library implementing the methodology. Results are shown for two example
scenarios (with and without climate policy cases) using the MESSAGE-GLOBIOM IAM
that satisfactorily harmonize over 96\% of the total emissions trajectories.
\end{abstract}

>>>>

\author[nies]{Shinichiro Fujimori}
\author[pbl]{Maarten van den Berg}
\author[pik]{David Klein}
\author[pnnl]{Steven J. Smith}
\author[pbl]{Detlef P. van Vuuren}
\author[iiasa]{Keywan Riahi}

@@

\begin{abstract}
Emission harmonization refers to the process used to match results from
Integrated Assessment Model (IAM) GHG and air pollutants against a common source
of historical emissions trajectories. To date, harmonization has been performed
separately by individual modeling teams. For the hand-over of emission data for
the Shared Socio-economic Pathways (SSPs) to climate model groups, a new
automated automatized approach was developed and used based upon commonly agreed
upon algorithms. This work describes a novel methodology for determining such
harmonization methods and an open-source Python software library implementing
the methodology. Results are shown for two example scenarios (with and without
climate policy cases) using the MESSAGE-GLOBIOM IAM that satisfactorily
harmonize over 96\% of the total emissions trajectories while having a
negligible effect on key long-term climate indicators. This new capability
enhances the comparability across different models, increases transparency and
robustness of results, and allows other teams to easily participate in
intercomparison exercises by using the same harmonization mechansim.
\end{abstract}
